%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{siunitx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\LARGE\scshape Vivek Vardhan Maharana} \\ \vspace{2pt}
    \small \raisebox{-0.1\height}\faPhone\ +91-8249379094 ~ \href{mailto:vivekvardhan2000@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{vivekvardhan2000@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/vivek-vardhan-maharana/}{\raisebox{-0.2\height}\faLinkedin\ \underline{vivek-vardhan-maharana}}  ~
    \href{https://github.com/VivekMaharana87}{\raisebox{-0.2\height}\faGithub\ \underline{VivekMaharana87}}
    \vspace{-8pt}
\end{center}


%------SUMMARY-------
\section{Summary}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{{Results-driven technology professional with 2+ years of experience in API development, automation, and scalable systems. Proven ability to deliver high-impact solutions, collaborate with global teams, solve complex problems, and drive performance optimization with continuous improvement in fast-paced environments.} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Deloitte Consulting | Business Analyst}{Jan 2024 -- Feb 2026}
      {Hyderabad, India}{}
      \resumeItemListStart
        \resumeItem{Received Applause Award for leading bi-weekly client solution playbacks.}
        \resumeItem{Delivered end-to-end UKG WFC to UKG Dimensions migration for a 200K+ employee client, developing Boomi integrations and cutting high-volume integration execution time from 8 hours to 48 minutes.}
        \resumeItem{Led cross-functional coordination and stakeholder meetings across multiple WFM and HCM implementations for Fortune 500 healthcare, banking, retail, and agriculture clients.}
        \resumeItem{Served as LSPOC for the Hyderabad Culture Team, coordinating leadership interactions, cross-location events, cultural celebrations, and PRD activities.}
      \resumeItemListEnd

    \resumeSubheading
      {Siemens | Frontend Development Intern}{May 2022 -- July 2022}
      {Bengaluru, India}{}
        \resumeItemListStart
            \resumeItem{Implemented data source from Grafana Labs API in Python for data extraction from PLC to store and monitor data.}
            \resumeItem{Used Matplotlib and Pandas to sub-sample the data points and visualize the data to display in a single dashboard}
        \resumeItemListEnd

    \resumeSubheading
      {Samsung - Reseach \&\ Development | Research Intern}{June 2021 -- Jan 2022}
      {Bengaluru, India}{}
        \resumeItemListStart
            \resumeItem{Designed models that allowed for multiple iterations to refine denoising process and improve the overall image quality.}
            \resumeItem{Reduced grain in the optimized enhanced images by implementing various ML techniques}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Image Pre-processing and Noise reduction using MIRNet and Autoencoders} $|$ \emph{Research Paper}}{}
          \resumeItemListStart
            \resumeItem{Led a team of 4 incorporating contextual information through attention mechanisms on TM-DIED dataset that combines iterative residual learning and multi-scale feature extraction.}
            \resumeItem{Proposed a CNN + Dual Attention model for the 4-class problem allowing for developing efficient architectures that balances computational complexity and real-time performance, allowing for noise reduction.}
          \resumeItemListEnd
          \vspace{-20pt}
        \resumeProjectHeading
          {\textbf{Survival Prediction in Titanic Ship} $|$ \emph{Kaggle}}{}
          \resumeItemListStart
            \resumeItem{Developed prediction algorithm with an accuracy score of \SI{93.02}{\percent} (gain of +\SI{7.44}{\percent} than base paper) in Kaggle dataset.}
            \resumeItem{Received a Silver badge globally for the Efficient proposed approach implementing Logistic Regression using Python.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-16pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C++, JavaScript, Groovy, OpenCV, SQL, HTML/CSS} \\
     \textbf{Developer Tools}{: Postman, Kleopatra, WinSCP, VS Code, Eclipse, Excel, Visio, MySQL} \\
     \textbf{Web Technologies/Frameworks}{: GitHub, REST APIs, UKG Pro WFM, Boomi Atomsphere, API Management, XML/JSON Transformation, Error Handling, Performance Optimization} \\
     \textbf{Automation \&\ AI}{: Smartsheet, Jira, Conversational AI Agents, Process Automation, Workflow Optimization} \\
     \textbf{CS Fundamentals}{: OOPS, DBMS, Operating System, Computer Networks} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Accomplishments \&\ Certification}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{UKG}{: Certified Boomi Integration Developer} \\
     \textbf{Boomi}{: Professional Integration Developer, Associate Integration Developer} \\
     \textbf{HacktoberFest by Digital Ocean}{: Contributed to open-source projects with 6 PRs accepted out of 18 submissions, collaborating with global peers and identifying reported GitHub issues and bugs.} \\
     \textbf{TedX SOA University}{: Director of Post Production; co-led operations with brands like Social Nation.} \\
     \textbf{Microsoft Azure Developer League}{: Earned 240+ badges and 60 medals by completing all 7 Azure Developer League challenges, gaining hands-on experience in identity, governance, privacy, and compliance.} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------EDUCATION-----------
\section{Education}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     {Bachelors of Technology (Computer Science and IT) $|$ {I.T.E.R} $|$ {SOA} $|$ {CGPA : 8.4/10} \hfill 2023} \\
     {12th Science $|$ DAV Public School, Chandrasekharpur $|$ \SI{90}{\percent} aggregate \hfill 2019} \\
     {10th CBSE $|$ DAV Public School, Chandrasekharpur $|$ \SI{93.1}{\percent} aggregate \hfill 2017} \\
    }}
 \end{itemize}
 \vspace{-16pt}

\end{document}
